### 2016-09-30 categories.tex
Add a citation for Xy-pic
Fix typo

Automatic typesetting of diagrams takes a \texttt{Diagram} and produces \LaTeX{}
code using the \texttt{Xy-pic} package.  Typesetting is done in two stages:
layout and generation of \texttt{Xy-pic} code.  The layout stage is taken care
of by the class \texttt{DiagramGrid}, which takes a \texttt{Diagram} and lays out
the objects in a grid, trying to reduce the average length of the arrows in the
final picture.  By default, \texttt{DiagramGrid} uses a series of triangle-based
heuristics to produce a rectangular grid.  A linear layout can also be imposed.
Furthermore, groups of objects can be given; in this case, the groups will be
treated as atomic cells, and the member objects will be typeset independently of
the other objects.

The second phase of diagram typesetting consists in actually drawing the picture
and is carried out by the class \texttt{XypicDiagramDrawer}.  An example of a
diagram automatically typeset by \texttt{DiagramgGrid} and
\texttt{XypicDiagramDrawer} in given in Figure~\ref{fig:cat:loops}.
\begin{figure}[h]
  \centerline{
    \xymatrix{
      A \ar[r]_{f} \ar@/^3mm/[rr]^{h_{2}} \ar@(u,l)[]^{l_{A}} \ar@/^3mm/@(l,d)[]^{n_{A}} & B \ar[d]^{g} & D \ar[l]^{k} \ar@/_7mm/[ll]_{h} \ar@/_11mm/[ll]_{h_{1}} \ar@(r,u)[]^{l_{D}} \ar@/^3mm/@(d,r)[]^{n_{D}} \\
      & C \ar@(l,d)[]^{l_{C}} \ar@/^3mm/@(d,r)[]^{n_{C}} &
    }
  }
  \caption{An automatically typeset commutative diagram}\label{fig:cat:loops}
\end{figure}

>>>>

Automatic typesetting of diagrams takes a \texttt{Diagram} and produces \LaTeX{}
code using the \texttt{Xy-pic} package~\cite{rose1999xy}.  Typesetting is done in two stages:
layout and generation of \texttt{Xy-pic} code.  The layout stage is taken care
of by the class \texttt{DiagramGrid}, which takes a \texttt{Diagram} and lays out
the objects in a grid, trying to reduce the average length of the arrows in the
final picture.  By default, \texttt{DiagramGrid} uses a series of triangle-based
heuristics to produce a rectangular grid.  A linear layout can also be imposed.
Furthermore, groups of objects can be given; in this case, the groups will be
treated as atomic cells, and the member objects will be typeset independently of
the other objects.

The second phase of diagram typesetting consists in actually drawing the picture
and is carried out by the class \texttt{XypicDiagramDrawer}.  An example of a
diagram automatically typeset by \texttt{DiagramgGrid} and
\texttt{XypicDiagramDrawer} is given in Figure~\ref{fig:cat:loops}.
\begin{figure}[h]
  \centerline{
    \xymatrix{
      A \ar[r]_{f} \ar@/^3mm/[rr]^{h_{2}} \ar@(u,l)[]^{l_{A}} \ar@/^3mm/@(l,d)[]^{n_{A}} & B \ar[d]^{g} & D \ar[l]^{k} \ar@/_7mm/[ll]_{h} \ar@/_11mm/[ll]_{h_{1}} \ar@(r,u)[]^{l_{D}} \ar@/^3mm/@(d,r)[]^{n_{D}} \\
      & C \ar@(l,d)[]^{l_{C}} \ar@/^3mm/@(d,r)[]^{n_{C}} &
    }
  }
  \caption{An automatically typeset commutative diagram}\label{fig:cat:loops}
\end{figure}
